Supermassive black hole and host bulge affairs \\ I. True to life galaxy decomposition.

### 2015-05-28 papers/data_paper/datapaper.tex
cardioiloveu

\subsubsection{S\'ersic/core-S\'ersic classification}
\label{sec:corser}
Core-S\'ersic galaxies \citep{grahamguzman2003,graham2003coresersicmodel,trujillo2004coresersicmodel} are galaxies (or bulges) 
with partially depleted cores, 
i.e.~a central deficit of light relative to the inward extrapolation of their outer S\'ersic light profile. 
Such deficits were first noted and researched by \cite{kingminkowski1966}.
S\'ersic galaxies, instead, do not exhibit such central stellar deficits.
Partially depleted cores, as measured from high-resolution observations, have typical sizes of a few tens of parsecs
\citep{dullograham2013cores,rusli2013}.
The majority are thus unresolved in our image mosaics. 
We masked these unresolved cores (identified in high-resolution images, see Table \ref{tab:sample}) by excluding the surface brightness profile 
within 3 PSF's $FWHM$ from the galaxy center.
In case of cores with sizes exceeding the PSF's $FWHM$, we excluded the data points within the size of the core 
plus 3 PSF's $FWHM$.
The S\'ersic/core-S\'ersic classification presented in this work (Table \ref{tab:sample}, column 5)
comes from the compilation of \citet{savorgnangraham2014},
who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
When no high-resolution image analysis was available from the literature, 
they inferred the presence of a partially depleted core based on the stellar velocity dispersion, $\sigma$:
a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$.
This resulted in us assigning cores to just 2 galaxies using this alternative method when 
no high resolution image was available.

@@

  BTW, if we wanna test the two phase formation scenario, we should care more about the halos...
  at which effective radius does the halo begin?
  what is the ratio of the mass in the galaxy or in the halo?

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m89_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M89.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M89.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-halo  & $29.0$  &  $4.6$ \\
  T.W. 1D eq.  & S-bul + e-halo  & $28.2$  &  $5.1$ \\
  %T.W. 2D	&   & $$  & $$  &  $$ \\
  \hline
  &   & $$  &  $$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m89}
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3585_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 3585.}
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3607_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 3607.}
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3608_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 3608.}
  \end{center}
  \end{figure}

@@

  NGC 4151 is a face-on barred spiral galaxy that hosts a Seyfert AGN \citep{veroncettyveron2006} 
  and circumnuclear dust \citep{pott2010}.

  \cite{sani2011} fit this galaxy with a S\'ersic-bulge + exponential-disk + Gaussian-AGN model
  ($R_{\rm e} = 5''.4$, $n = 3.5$).
  \cite{gadotti2008} decomposed it into a S\'ersic-bulge + exponential-disk + S\'ersic-bar + PSF-AGN 
  ($R_{\rm e} = 4''.7$, $n = 3.0$).

  \emph{1D fit -- }
  embedded disk in the bulge,

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n4151_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 4151.}
  \end{center}
  \end{figure}

@@

  NGC 4473 is an elliptical galaxy with an embedded disk \citep{scorzabender1998,ledo2010}.

  \cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
  ($R_{\rm e} = 39''.6$, $n = 2.7$). 
  \cite{sani2011} used a S\'ersic-bulge model
  ($R_{\rm e} = 49''.3$, $n = 7.0$). 
  \cite{vika2012} fit this galaxy with a S\'ersic-bulge + mask-core 
  ($R_{\rm e} = 21''.3$, $n = 4.3$). 
  \cite{beifiori2012} adopted a S\'ersic-bulge + exponential-disk model 
  ($R_{\rm e} = 10''.6$, $n = 2.2$).  
  \cite{lasker2014data} described this galaxy with a single S\'ersic-bulge 
  ($R_{\rm e} = 27''.9$, $n = 5.1$).

  \emph{1D fit -- }
  TBD!! explain ellipticity profile...

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n4473_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 4473.}
  \end{center}
  \end{figure}

@@

  NGC 4564 is an edge-on lenticular galaxy.

  %\cite{grahamdriver2007} decomposed this galaxy into a S\'ersic-bulge + exponential-disk 
  %($R_{\rm e} = 4''.3$, $n = 3.2$). 
  \cite{fisherdrory2008} fit this galaxy with a S\'ersic-bulge + exponential-disk 
  ($R_{\rm e} = 8''.7$, $n = 3.7$). 
  %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
  %($R_{\rm e} = 25''.0$, $n = 7.0$).
  %\cite{vika2012} used a S\'ersic-bulge + exponential-disk model 
  %($R_{\rm e} = 3''.0$, $n = 3.7$).

  \emph{1D fit -- }
  The isophotal parameters do not show any evidence for embedded components.
  However, fitting NGC 4564 with a S\'ersic + exponential model results in bad residuals.
  In the unsharp mask, one can hardly glimpse an oval structure extending out to $R \lesssim 15''$.
  The addition of a Ferrer function to the model dramatically improves the fit and smoothes the residuals.
  Although the lack of strong evidence for the presence of a (faint) third component, 
  we prefer to model the lens with a Ferrer function 
  because of the notable improvement in the goodness of the global fit.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n4564_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 4564.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 4564.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d + F-l & $5.0$  &  $2.6$ \\
  T.W. 1D eq.  & S-bul + e-d + F-l & $6.0$  &  $3.0$ \\
  %T.W. 2D	&  & $$  &  $$ \\
  \hline
  GD07      & S-bul + e-d & $4.3$  &  $3.2$ \\
  S+11      & S-bul + e-d & $25.0$ &  $7.0$ \\
  V+12      & S-bul + e-d & $3.0$  &  $3.7$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n4564}
  \end{table}

@@

  NGC 4596 is an edge-on barred lenticular galaxy.

  %\cite{laurikainen2005} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Ferrer-bar + Ferrer-lens 
  %($R_{\rm e} = 2''.8$, $n = 1.4$). 
  %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk + Gaussian-bar 
  %($R_{\rm e} = 28''.0$, $n = 3.0$). 
  %\cite{vika2012} decomposed it into a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
  %($R_{\rm e} = 13''.2$, $n = 3.6$). 
  %\cite{beifiori2012} adopted a S\'ersic-bulge + exponential-disk model
  %($R_{\rm e} = 44''.9$, $n = 4.4$).

  \emph{1D fit -- }
  The morphology of this galaxy is quite complex. 
  The bar extends out to $R \lesssim 50''$ and concludes in two evident ansae.
  The large-scale disk features a wide ring that is responsible for the curvature in the light profile observed within 
  $60'' \lesssim R \lesssim 130''$ (see also \citealt{comeron2014}).
  An additional embedded disk-like component ($R \lesssim 15''$) can be recognized in the B4 profile and in the velocity map.
  The bump in the light profile within $60'' \lesssim R \lesssim 70''$ corresponds to the ansae of the bar.
  This data range has therefore been excluded from the fit.
  The large scale bar is fit with a Ferrer function and the inner disk with a S\'ersic profile.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n4596_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 4596.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 4596.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d + F-bar + G-r + S-id & $6.6$  &  $2.7$ \\
  T.W. 1D eq.  & S-bul + e-d + F-bar + G-r + S-id & $9.0$  &  $3.0$ \\
  %T.W. 2D	&  & $$  & $$  &  $$ \\
  \hline
  L+10      & S-bul + e-d + F-bar + F-l & $2.8$  &  $1.4$ \\
  S+11      & S-bul + e-d + G-bar & $28.0$  &  $3.0$ \\
  V+12      & S-bul + e-d + S-bar & $13.2$  &  $3.6$ \\
  B+12      & S-bul + e-d & $44.9$  &  $4.4$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n4596}
  \end{table}

@@

  NGC 4697 is an elliptical galaxy with an embedded disk \cite{scorzabender1995}.

  %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge model
  %($n = 4.0$).
  %\cite{sani2011} described it with a S\'ersic-bulge 
  %($R_{\rm e} = 100'.5$, $n = 5.0$). 
  %\cite{vika2012} proposed a single S\'ersic-bulge model 
  %($R_{\rm e} = 39''.1$, $n = 3.8$) 
  %or a S\'ersic-bulge + exponential-disk model 
  %($R_{\rm e} = 10''.0$, $n = 2.9$).
  %\cite{beifiori2012} chose a single S\'ersic-bulge 
  %($R_{\rm e} = 128''.7$, $n = 5.0$).
  %\cite{lasker2014data} decomposed NGC 4697 into a S\'ersic-bulge + exponential-disk + PSF-nucleus + S\'ersic-envelope 
  %($R_{\rm e} = 6''.3$, $n = 2.1$).

  \emph{1D fit -- }
  The velocity map and the unsharp mask of NGC 4697 clearly show 
  the presence of an intermediate-size disk embedded in the main spheroid.
  However, the ellipticity profile presents two peaks. 
  The peak at $R \sim 40''$ corresponds to the embedded disk already mentioned,
  while the peak at $R \sim 10''$ unveils a second inner disk-like component.
  After testing different decomposition models, 
  in which we fit the embedded disks with a set of different functions (exponential, S\'ersic, Ferrer)
  but we always described the main spheroidal component with a S\'ersic profile,
  we noticed that the bulge parameters did not vary significantly among the various decompositions.
  Our preferred model for NGC 4697 consists of a S\'ersic-bulge + 2 S\'ersic-inner disks.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n4697_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 4697.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 4697.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + 2 S-id & $239.3$  &  $7.2$ \\
  T.W. 1D eq.  & S-bul + 2 S-id & $226.4$  &  $6.7$ \\
  T.W. 2D      & S-bul + e-id	& $121.4$  &  $5.0$ \\
  \hline
  GD07  & S-bul & $-$  &  $4.0$ \\
  S+11  & S-bul & $100.5$  &  $5.0$ \\
  V+12  & S-bul & $39.1$  &  $3.8$ \\
  V+12  & S-bul + e-d & $10.0$  &  $2.9$ \\
  L+14  & S-bul + e-d + PSF-n + S-halo & $6.3$  &  $2.1$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n4697}
  \end{table}

@@

  NGC 4889 is the brightest member of the Coma cluster. 
  It is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.6$, \citealt{rusli2013}).

  %\cite{rusli2013} modeled NGC 4889 with a core-S\'ersic model 
  %($R_{\rm e} = 169''.2$, $n = 9.8$).

  \emph{1D fit -- }
  We excluded from the fit the innermost $6''.1$ because affected by the partially depleted core and
  we modeled the galaxy with a single S\'ersic profile.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 4889.}
  \end{center}
  \end{figure}

@@

  TBD!!! \\
  NGC 4945 is an edge-on, dusty spiral galaxy that hosts a Seyfert AGN \citep{lin2011}.

  \cite{kormendy2010} found that the bulge of NGC 4945 is best modeled with a low-$n$ S\'ersic function
  ($n = 1.3$).

  \emph{1D fit -- }
  Given the edge-on inclination of this object, the identification of a possible large-scale bar is complicated.
  The light profile has an obvious bump that could be interpreted in two different ways.
  The bump could be produced by a large-scale bar; 
  in this case, either the disk must have a truncation happening at a radius smaller than the length of the bar,
  or its light profile cannot be exponential (this condition can be caused by the high inclination of the galaxy).
  Alternatively, the bump could be due by the galaxy spiral arms, the disk has an exponential profile with no truncation
  and the galaxy has no bar.
  After checking that both scenarios result in similar best-fit parameters for the bulge, 
  we choose the second and simpler hypothesis.
  We exclude form the fit the data between $R \sim 100''-400''$, where the spiral arm would contribute to the galaxy light,
  and we also exclude the innermost $6''.4$ due to the presence of the AGN.
  Our final model for NGC 4945 consists of a S\'ersic-bulge + exponential-disk.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n4945_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 4945.}
  \end{center}
  \end{figure}

@@

  \emph{1D fit -- }

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n5077_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 5077.}
  \end{center}
  \end{figure}

>>>>

\subsubsection{S\'ersic/core-S\'ersic classification}
\label{sec:corser}
Core-S\'ersic galaxies \citep{grahamguzman2003,graham2003coresersicmodel,trujillo2004coresersicmodel} are galaxies (or bulges) 
with partially depleted cores, 
i.e.~a central deficit of light relative to the inward extrapolation of their outer S\'ersic light profile. 
Such deficits were first noted and researched by \cite{kingminkowski1966}.
S\'ersic galaxies, instead, do not exhibit such central stellar deficits.
Partially depleted cores, as measured from high-resolution observations, have typical sizes of a few tens of parsecs
\citep{dullograham2014cores,rusli2013}.
The majority are thus unresolved in our image mosaics. 
We masked these unresolved cores (identified in high-resolution images, see Table \ref{tab:sample}) by excluding the surface brightness profile 
within 3 PSF's $FWHM$ from the galaxy center.
In case of cores with sizes exceeding the PSF's $FWHM$, we excluded the data points within the size of the core 
plus 3 PSF's $FWHM$.
The S\'ersic/core-S\'ersic classification presented in this work (Table \ref{tab:sample}, column 5)
comes from the compilation of \citet{savorgnangraham2014},
who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
When no high-resolution image analysis was available from the literature, 
they inferred the presence of a partially depleted core based on the stellar velocity dispersion, $\sigma$:
a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$.
This resulted in us assigning cores to just 2 galaxies using this alternative method when 
no high resolution image was available.

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m89_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M89.
  M89 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. 
  The galaxy halo dominates the light at large radii, where the isophotes are significantly more elliptical than in the inner part of the galaxy. 
  The halo is modeled with an exponential function. 
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M89.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-halo  & $29.0$  &  $4.6$ \\
  T.W. 1D eq.  & S-bul + e-halo  & $28.2$  &  $5.1$ \\
  %T.W. 2D	&   & $$  & $$  &  $$ \\
  \hline
  S+11         & S-bul + e-d     & $24.3$  &  $4.0$ \\
  V+12         & S-bul           & $16.7$  &  $3.6$ \\
  B+12         & S-bul           & $45.2$  &  $4.3$ \\
  R+13         & S-bul + S-halo  & $19.8$  &  $3.8$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m89}
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3585_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 3585. 
  NGC 3585 is an elliptical galaxy with an embedded disk \cite{scorzabender1995}. 
  The embedded disk is visible in the unsharp mask and modeled with an exponential function. }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3585.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-id & $105.0$  &  $5.2$ \\
  T.W. 1D eq.  & S-bul + e-id & $86.3$  &  $6.3$ \\
  \hline
  S+11         & S-bul + e-d      & $15.5$   &  $2.5$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3585}
  \tablecomments{
  S+11 obtained smaller estimates of the effective radius and S\'ersic index because
  they oversubtracted a large-scale disk.
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3607_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 3607. 
  NGC 3607 is an elliptical galaxy with an embedded disk. 
  The velocity map shows rotation only within $R_{\rm maj} \lesssim 20''$. 
   }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3607.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-id & $69.3$  &  $5.5$ \\
  T.W. 1D eq.  & S-bul + e-id & $65.5$  &  $5.6$ \\
  T.W. 2D      & S-bul + e-id & $60.0$  &  $5.3$ \\
  \hline
  L+10	   & S-bul + e-d      & $6.5$   &  $1.5$ \\
  S+11	   & S-bul + G-n      & $44.6$  &  $5.0$ \\
  B+12	   & S-bul	      & $56.3$  &  $4.7$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3607}
  \tablecomments{L+10 obtained the smallest estimates of the effective radius and S\'ersic index because
  they oversubtracted a large-scale disk.
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3608_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 3608.
  NGC 3608 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013} 
  and a kinematically decoupled core. 
  We find unnnecessary masking the nuclear region of this galaxy and we fit the light profile with a single S\'ersic model.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3608.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul & $47.5$  &  $5.2$ \\
  T.W. 1D eq.  & S-bul & $43.4$  &  $5.7$ \\
  T.W. 2D      & S-bul & $62.0$  &  $7.0$ \\
  \hline
  S+11         & S-bul            & $56.4$  &  $6.0$ \\
  B+12         & S-bul            & $182.2$  &  $9.0$ \\
  R+13         & core-S\'ersic    & $56.9$  &  $6.3$ \\
  L+14         & S-bul            & $48.9$  &  $6.6$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3608}
  \tablecomments{B+12 obtained the largest estimates of the effective radius and S\'ersic index, 
  but the reasons for this are not clear. }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n4151_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 4151.
  NGC 4151 is a face-on barred spiral galaxy that hosts a Seyfert AGN \citep{veroncettyveron2006} 
  and circumnuclear dust \citep{pott2010}.
  The nucleus of this galaxy is very bright and the IRAf task {\tt ellipse} fails at fitting the isophotes within $R_{\rm maj} < 4''$, 
  thus our light profile starts at $R_{\rm maj} \sim 4''$. 
  The bar is fit with a low-$n$ S\'ersic profile.  
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 4261.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d + S-bar [+ m-n] & $7.6$  &  $1.4$ \\
  T.W. 1D eq.  & S-bul + e-d + S-bar [+ m-n] & $6.8$  &  $1.9$ \\
  %T.W. 2D      & S-bul + e-d + S-bar + m-n & $$  &  $$ \\
  \hline
  S+11         & S-bul + e-d + G-n         & $5.4$  &  $3.5$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n4151}
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n4473_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 4473.
  NGC 4473 is an elliptical galaxy with an embedded disk \citep{ledo2010}.
  The disk is clearly visible in the velocity map. 
  We account for a nuclear excess of light by adding a narrow Gaussian function to the model.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 4473.}
  \begin{center}
  \begin{tabular}{llccc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-id + G-n & $45.9$  &  $2.3$ \\
  T.W. 1D eq.  & S-bul + e-id + G-n & $36.9$  &  $2.9$ \\
  %T.W. 2D	&  & $$  &  $$ \\
  \hline
  GD07      & S-bul                 & $39.6$   &  $2.7$ \\
  S+11      & S-bul                 & $49.3$   &  $7.0$ \\
  V+12      & S-bul + m-c           & $21.3$   &  $4.3$ \\
  B+12      & S-bul + e-d           & $10.6$   &  $2.2$ \\
  L+14      & S-bul                 & $27.9$   &  $5.1$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n4459}
  \tablecomments{
  B+12 obtained the smallest estimates of the effective radius and S\'ersic index because they oversubtracted a large-scale disk. 
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n4564_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 4564.
  NGC 4564 is an edge-on lenticular galaxy.
  In the unsharp mask, one can glimpse an oval structure extending out to $R_{\rm maj} \lesssim 15''$ (see the peak in the B4 profile).
  Fitting NGC 4564 with a S\'ersic + exponential model produces bad residuals.
  The addition of a Ferrer function to the model dramatically improves the fit and smoothes the residuals.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 4564.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d + F-l & $5.0$  &  $2.6$ \\
  T.W. 1D eq.  & S-bul + e-d + F-l & $6.0$  &  $3.0$ \\
  %T.W. 2D	&  & $$  &  $$ \\
  \hline
  GD07      & S-bul + e-d & $4.3$  &  $3.2$ \\
  S+11      & S-bul + e-d & $25.0$ &  $7.0$ \\
  V+12      & S-bul + e-d & $3.0$  &  $3.7$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n4564}
  \tablecomments{The most dicrepant results are obtained by S+11, although they used the same model as GD07 and V+12. }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n4596_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 4596.
  NGC 4596 is an edge-on barred lenticular galaxy.
  The morphology of this galaxy is quite complex. 
  The bar extends out to $R_{\rm maj} \lesssim 50''$ and concludes in two evident ansae.
  The large-scale disk features a wide ring that is responsible for the curvature in the light profile observed within 
  $60'' \lesssim R_{\rm maj} \lesssim 130''$ (see also \citealt{comeron2014}).
  An additional embedded disky component ($R_{\rm maj} \lesssim 15''$) can be recognized in the B4 profile and in the velocity map.
  The bump in the light profile within $60'' \lesssim R_{\rm maj} \lesssim 70''$ corresponds to the ansae of the bar.
  This data range is excluded from the fit.
  The large scale bar is fit with a Ferrer function and the inner disk with a low-$n$ S\'ersic profile.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 4596.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d + F-bar + G-r + S-id & $6.6$  &  $2.7$ \\
  T.W. 1D eq.  & S-bul + e-d + F-bar + G-r + S-id & $9.0$  &  $3.0$ \\
  %T.W. 2D	&  & $$  & $$  &  $$ \\
  \hline
  L+10      & S-bul + e-d + F-bar + F-l & $2.8$  &  $1.4$ \\
  S+11      & S-bul + e-d + G-bar & $28.0$  &  $3.0$ \\
  V+12      & S-bul + e-d + S-bar & $13.2$  &  $3.6$ \\
  B+12      & S-bul + e-d & $44.9$  &  $4.4$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n4596}
  \tablecomments{
  B+12 fit nor the bar neither the inner disk and obtained the largest estimates of the bulge effective radius and S\'ersic index.
  The models of S+11 and V+12 account for the bar and thus result in lower estimates of the bulge effective radius and S\'ersic index.
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n4697_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 4697.
  NGC 4697 is an elliptical galaxy with an embedded disk \citep{scorzabender1995}.
  The velocity map and the unsharp mask of NGC 4697 clearly show 
  the presence of an intermediate-size disk embedded in the galaxy's spheroidal component.
  However, the ellipticity profile presents two peaks. 
  The peak at $R_{\rm maj} \sim 40''$ corresponds to the intermediate-size embedded disk just mentioned,
  while the peak at $R_{\rm maj} \sim 10''$ unveils a smaller inner disk.
  After testing different decomposition models, 
  in which we fit the two embedded disks with different functions (exponential, S\'ersic, Ferrer),
  while always describing the main spheroidal component with a S\'ersic profile,
  we noticed that the spheroid parameters do not significantly vary among the various decompositions.
  Our preferred model for NGC 4697 consists of a S\'ersic-bulge + 2 S\'ersic-inner disks.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 4697.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + 2 S-id & $239.3$  &  $7.2$ \\
  T.W. 1D eq.  & S-bul + 2 S-id & $226.4$  &  $6.7$ \\
  T.W. 2D      & S-bul + e-id	& $121.4$  &  $5.0$ \\
  \hline
  GD07  & S-bul & $-$  &  $4.0$ \\
  S+11  & S-bul & $100.5$  &  $5.0$ \\
  V+12  & S-bul & $39.1$  &  $3.8$ \\
  V+12  & S-bul + e-d & $10.0$  &  $2.9$ \\
  L+14  & S-bul + e-d + PSF-n + S-halo & $6.3$  &  $2.1$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n4697}
  \tablecomments{
  In both their models, V+12 underestimated the effective radius and the S\'ersic index because of the small radial range of their data. 
  L+14 oversubtracted a large-scale disk and a halo, and thus underestimated the spheroid effective radius and the S\'ersic index. 
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 4889.
  NGC 4889 is the brightest member of the Coma cluster. 
  It is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. % ($R_{\rm break} = 1''.6$, \citealt{rusli2013}).
  We exclude from the fit the innermost $6''.1$ and
  we successfully model the galaxy with a single S\'ersic profile.
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n4945_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 4945.
  NGC 4945 is an edge-on, dusty spiral galaxy that hosts a Seyfert AGN \citep{lin2011}.
  The light profile has an obvious bump that can be ascribed to a bar.
  This bumb cannot be easily modeled with a Ferrer function, thus we exclude form the fit the data in the range $100'' \lesssim R_{\rm maj} \sim 400''$.
  We also exclude the data within the innermost $6''.4$ due to the contribution from the AGN.
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n5077_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 5077. 
  NGC 5077 is an elliptical galaxy with an unresolved partially depleted core \citep{trujillo2004coresersicmodel}. 
  We mask the data within the innermost $6''.1$ and fit the galaxy with a S\'ersic profile. }
  \end{center}
  \end{figure}
